### 2016-01-18 paper/intro.tex
adding draft outline

>>>>

\subsection{draft outline}
\bit 
\item background/previous work? to put this work in context?
\item mathematical formulation
  \bit
  \item define inverse problem and qoi
  \item derive error estimate
  \item caveats (models to which this can be applied, no guarantee that mixed model will be worth the cost to obtain, no bounds on accuracy of estimate in nonlinear case)
  \item relation to mesh refinement
  \item How does this compare to just using Oden et al's method (multimodel, foward with QoI) and replacing forward PDEs with optimality system of inverse problem? (Oden's gets you second-order in error psiHF-psiLF, but this one gets third, though you have to compute the super-adjoint...linear solve, though...big system, but linear...)
  \eit
\item numerical results (perhaps not include all of these...)
  \bit
  \item convection-diffusion(-reaction)
    \bit
    \item interpretation of error estimate breakdown (interaction of QoI with observations)
    \item large reaction term: MF model more cooperative with nonlinear solver
    \eit
  \item convection-diffusion-reaction, field vs scalar description of parameters
    \bit
    \item interface question: do we enforce continuity between the two models' parameters?
    \item chose to have one 'scalar' parameter, so all sections where the LF used shared same single parameter; is this necessarily the best choice?
    \item chose to enforce continuity (easier to implement; field representation required to be continuous); algorithm wanted 60/40 HF/LF mix
    \eit
  \item alternate/additional example: use setup from B+V? navier-stokes and another model? 
    \bit
    \item potential flow? model flow as sum of elementary flows; but then parameters would be magnitudes of elementary flows, which has no spatial location...is that a problem for the algorithm or just for interpreting error breakdown?
    \item there would still be the question of how to interface the models...
    \eit
  \item have a separate section to address questions of how to mix models? (interfaces, whether 'scalar' parameter should be the same everywhere)
  \eit
\item conclusion...what goes in this section usually? summary and directions for future work?
\eit
